---
title: "Final Project"
author: "Akarawee Chavanarorkrat"
output:
  html_document:
    df_print: paged
---

# Questions

#### I would like to find out the attribute of a wine given in the data that lead to the wine score. What makes a wine special.

#### My hypothesis are

```
  :1 Price
  :2 Description provided by the critic.
```
## Download the library
```{r}
library(tidyverse)#load tidyverse
library(DataComputing)#load Datacomputing
library(leaflet)# load Leaflet map
library(tidytext)#load tidytext for word extraction
options(warn=-1) # to get rid of some warnings that can be remove
```
```
-I would like to do an informative research on wine price which include appreciation and depreciation. What factor drives wine price of the wine up and down? What makes wine A more expensive that wine B?
-The data is from Kaggle.
-The data was collected by winemag a wine tasting magazine.
-Each case represents each wine.
-There are over 130 thousand cases.
-Wine region wine score wine price and variant
```

# Step 1 
## Download the data
```{r}
Wine<- read.csv(file = 'winemag-data-130k-v2.csv',header = TRUE, stringsAsFactors = FALSE) # Read the wine file to Wine
Wine
```


# Step 2
## Visualizing the data and understanding the data
#### Because some wine didn't come with the price tag whether it's too old for the price tag to be relevent or it was a barrel sample(pre-production)

```
Prepare the data for further step
Find the average price of wine
Remove all the NA
```
```{r}
wine2<-na.omit(Wine)#na.omit remove all the NA in price 
avg<-
wine2%>%
group_by(country)%>% #we want to see the per country part
summarise (avg = mean(price),Score =mean(points)) #average of both price and points
avg
```
```{r}
ggplot(data=avg,aes(x=avg,y=Score, ymin=80))+geom_point() # try to look for a correlation between price and score with the average of the country
```
```
finding 95 percentile of the wine price

Seems to have a corelation between price and points on the average of each country
```
```{r}
wine2 %>% 
    group_by(country) %>%  
    summarise(quantile = scales::percent(c(0.95)),# scales to find the price for each percential and also score. I end up satisfy with the top 5 because of the score being average of 94 in the US and France(see the scale on Readme.md)
              price = quantile(price, c(0.95)),score = quantile(points, c(0.95)))
```

```
Finding bottom 5
```
```{r}
wine2 %>% 
    group_by(country) %>%  
    summarise(quantile = scales::percent(c(0.05)),# scales to find the price for each percential and also score. I end up satisfy with the bottom 5 because of the score being average of 84 in France and 83 in the US(see the scale on Readme.md)
              price = quantile(price, c(0.05)),score= quantile(points, c(0.05)))
```
```
As we can see that the scale of the wine is not 0-100 points but start approximately 80
So when we create a graph for the wine we must set the scale to 80-100
```
```{r}
p95<-
 wine2 %>% filter(points > quantile(points, 0.95))
p05<-
 wine2 %>% filter(points < quantile(points, 0.05))
```
```{r}
#use warn because to amount of warning on top of the GGplot preventing me to vitualizing the data
warn<-ggplot(data=p95,aes(x=price,y=points,ymin=96, ymax=100))+geom_point()+facet_wrap(~country,ncol=4) + stat_smooth(method="auto")
suppressWarnings(print(warn))
```
```{r}
warn<-ggplot(data=p05,aes(x=price,y=points,ymin=80, ymax=100))+geom_point()+facet_wrap(~country,ncol=4)+ stat_smooth(method="auto") 
suppressWarnings(print(warn))
```
```
There is no linear corelation with the price and point but the average of top 5 and bottom 5 vary by between 20 to 70 usd to the higher point wine
```

# Step 3
## Focus(America)

```
Focus on the American wine Because 
  1. American wine can be found easily here in the United States
  2. Can easily compare because in an area for example NAPA valley there is a production of both cheap and expensive wine
  3. Good split between the top 5 and bottom 5 2793 and 2784
```
```{r}
filtered95 <- p95 %>% # filter the US
  filter(country == "US")
```
```{r}

tokenized_comments95 <- filtered95 %>% 
  select(description, designation, points, price, province, region_1, variety, winery) %>%
  unnest_tokens(word, description) %>% #take each word from the description to the word bank
  anti_join(stop_words) %>%
  filter(word != "wine") %>%
  filter(province != "America")%>%
  group_by(province, word) %>%
  tally()

tokenized_comments95 %>% glimpse() #show each word
```

```{r}
tokenized_comments95 %>%
  group_by(province) %>%
  top_n(15) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = reorder(word, n), y = n, fill = factor(province))) +
  geom_bar(stat = "identity") +#bar chart for top words of each region
  theme(legend.position = "none") +
  facet_wrap(~ province, scales = "free") + 
  coord_flip() +
  labs(x = "Frequency",
       y = "Top words",
       title = "Top 5 Percent US wine",
       subtitle = "")
```
```{r}
filtered05 <- p05 %>%
  filter(country == "US")
```
```{r}

tokenized_comments05 <- filtered05 %>%
  select(description, designation, points, price, province, region_1, variety, winery) %>%
  unnest_tokens(word, description) %>% #take each word from the description to the word bank
  anti_join(stop_words) %>%
  filter(word != "wine") %>%
  filter(province != "America")%>%
  group_by(province, word) %>%
  tally()

tokenized_comments05 %>% glimpse()#show each word
```
```{r}
tokenized_comments05 %>%
  group_by(province) %>%
  top_n(15) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = reorder(word, n), y = n, fill = factor(province))) +
  geom_bar(stat = "identity") +#bar chart for top words of each region
  theme(legend.position = "none") +
  facet_wrap(~ province, scales = "free") + 
  coord_flip() +
  labs(x = "Frequency",
       y = "Top words",
       title = "Bottom 5 Percent US wine",
       subtitle = "")
```

```
As we can see the top 5 percent of wine from the United States are from the 4 states(California, New York, Oregon, and Washington)
```
```{r}
latlong<- read.csv(file = 'statelatlong.csv',header = TRUE, stringsAsFactors = FALSE) #read the latitude longitude data to plot on leaflet
latlong
```

Start with Bottom 5 Wine
```{r}
wineUS05<-
tokenized_comments05 %>% 
  inner_join(latlong,by = c("province" = "City"))#join the data so the city can have the coordinate

```
```{r}
wineUS051<- wineUS05%>%
    group_by(province)%>%
    summarise(max(n),)
wineUS05 <-wineUS051%>%
  left_join(wineUS05, by = c('province'='province', 'max(n)'='n'))#taking the wine data to the word count data
wineUS05<-
select(wineUS05,-c(State))
```
```{r}
# Show the data map of the top word through the region
leaflet(data = wineUS05) %>% addTiles() %>% 
  addMarkers(~Longitude, ~Latitude, popup = ~word, label = ~word)

```
Top 5 wine
```{r}
wineUS95<-
tokenized_comments95 %>% 
  inner_join(latlong,by = c("province" = "City"))#join the data so the city can have the coordinate

```
```{r}
wineUS951<- wineUS95%>%
    group_by(province)%>%
    summarise(max(n),)
wineUS95 <-wineUS951%>%
  left_join(wineUS95, by = c('province'='province', 'max(n)'='n'))#taking the wine data to the word count data
wineUS95<-
select(wineUS95,-c(State))
```
```{r}
# Show the data map of the top word through the region
leaflet(data = wineUS95) %>% addTiles() %>%
  addMarkers(~Longitude, ~Latitude, popup = ~word, label = ~word)

```

**Seems like for even the bottom 5 the word is very similar to the top 5 but you can see that some word such as "faint, kicking, sour" is still appear in the top 5 but less so than the bottom 5**

```{r}
wineUS05 %>%
     pivot_wider(names_from = word, values_from = 'max(n)')# using pivot wider to help visualize the important keyword
```
```
There are 42 different words from the Bottom 5 and most of it are NA due to the fact that most of the states only make one wine and it wasn't rated highly

The word that appear the most is flavors and palate
```

```{r}
wineUS95 %>%
     pivot_wider(names_from = word, values_from = 'max(n)')# using pivot wider to help visualize the important keyword
```
### Finding frequency of the word in the whole bottom and top 5
```
The top 5 wine is also have a lot of flavors and palate but also the 'fruit' which is absent in the bottom 5 I suspect that bottom 5 wine do have decent taste but lack the fruit flavor
```
```{r}
filtered05 %>% 
    filter(grepl('faint|kicking|sour', description, ignore.case = TRUE))#regular expression to find the wine with the word describe
```
```
210 out of 2793 bottom wine contains which is 7.5 percent
```
```{r}
filtered95 %>% 
    filter(grepl(' faint| kicking| sour', description, ignore.case = TRUE))#regular expression to find the wine with the word describe
```
```
140 out of 2784 top wine contains which is 5 percent
```

```{r}
filtered05 %>% 
    filter(grepl('fruit', description, ignore.case = TRUE))#regular expression to find the wine with the word describe
```

```
728 out of 2793 wine contain which is 26 percent
```

```{r}
filtered95 %>% 
    filter(grepl('fruit', description, ignore.case = TRUE))#regular expression to find the wine with the word describe
```
```
1140 out of 2784 wine contain which is 41 percent
```
```
We then try to compare the 2 word to word
```

```{r}
compare_token <-tokenized_comments05%>%
  inner_join(tokenized_comments95, by = c('province'='province', 'word'='word'))%>%
  mutate(difference = (n.y/n.x))%>%#mutate the ratio of the top and bottom wine
  arrange(desc(difference))
compare_token
```

```
The word such as develop, refined, perfect, delicius, elegance can be found much more promenently in the top wine
```
```{r}
compare_token <-tokenized_comments95%>%
  inner_join(tokenized_comments05, by = c('province'='province', 'word'='word'))%>%
  mutate(difference = (n.y/n.x))%>%#mutate the ratio of the top and bottom wine
  arrange(desc(difference))
compare_token
```

```
The word such as Thin, simple, un ripe, dull, harsh can be found much more promenently in the bottom wine
```
```{r}
filtered05%>%
  summarise (avg = mean(price),Score =mean(points)) #mean price and points
```
```{r}
filtered95%>%
  summarise (avg = mean(price),Score =mean(points))# mean price and points
```
```
Price difference of 55 usd and the score difference of 12
```
# Step 4
## Conclusion

```
With the data from step 3 it seems to suggest that 
  1.Wine with top wine with high score tends to have a description that is more positive such as develop, refined, perfect, delicius, elegance.
  Wine with lower quality such as the bottom 5 tend to have a very neutral to negative description Thin, simple, un ripe, dull, harsh
  The word can also be on either the bottom or top so it's not a sure thing 
  2. Wine that are more expensive tend to score higher than the cheaper counter part (this could imply that the price affect the score because people might bias toward more expensive comodity) The price is not the sure indication of the quality as you can see that some cheap wine can score very highly and vise versa.
  
```
